Implementing Change in Multi-paradigm Environments, a Case Study

### 2015-02-17 rmtw/a3/latex8.tex
YOLO

\title{Assignment 3}

@@

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development[CITE] to be a development paradigm. In this study we use the term manual coding to mean development without the use of any particular paradigm. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

@@

\SubSection{Motivation for Research}
Performing this study would therefore (XXX same) be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.

>>>>

\title{Implementing Change in Multi-paradigm Environments, a Case Study}

@@

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development to be a development paradigm. In this study we use the term manual coding to describe development without the use of any particular paradigm. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

@@

\SubSection{Motivation for Research}
A major motivation for this study is to fill a gap in the literature, since there is no previous research which analyses how change is managed in multi-paradigm settings. Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.
